Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny

### 2018-08-10 tex/revised_manuscript.tex
editor review

\section*{Funding statement}
	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
	There was no additional external funding received for this study.

@@

%M. ampullaceus
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure8.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure9.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure10.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
	\label{fig:ampullaceus_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure11.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:ampullaceus_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure12.jpg}
	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
	\label{fig:ampullaceus_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure13.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
	\label{fig:ampullaceus_lamina}
\end{figure}

%M. franko
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure14.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure15.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure16.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
	\label{fig:franko_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure17.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:franko_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure18.jpg}
	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
	\label{fig:franko_maxilla}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure19.jpg}
	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:franko_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure20.jpg}
	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:franko_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure21.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:franko_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure22.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:franko_aedeagus}
\end{figure}

%M. sculptilis
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure23.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure24.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure25.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
	\label{fig:sculptilis_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure26.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:sculptilis_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure27.jpg}
	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:sculptilis_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure28.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:sculptilis_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure29.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
	\label{fig:sculptilis_aedeagus}
\end{figure}

%M. tylotos
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure30.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure31.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure32.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
	\label{fig:tylotos_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure33.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
	\label{fig:tylotos_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure34.jpg}
	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
	\label{fig:tylotos_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure35.jpg}
	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
	\label{fig:tylotos_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure36.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
	\label{fig:tylotos_lamina}
\end{figure}

>>>>

@@

%M. ampullaceus
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure8.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure9.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure10.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure11.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure12.jpg}
	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure13.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:ampullaceus_lamina}
\end{figure}

%M. franko
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure14.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:franko_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure15.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:franko_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure16.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:franko_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure17.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:franko_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure18.jpg}
	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:franko_maxilla}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure19.jpg}
	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:franko_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure20.jpg}
	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:franko_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure21.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:franko_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure22.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view. Photo credit: Andrew Jansen.}
	\label{fig:franko_aedeagus}
\end{figure}

%M. sculptilis
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure23.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure24.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure25.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure26.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure27.jpg}
	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure28.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_lamina}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{sideways}
		\includegraphics[width=0.95\textheight]{figure29.jpg}
	\end{sideways}
	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view. Photo credit: Andrew Jansen.}
	\label{fig:sculptilis_aedeagus}
\end{figure}

%M. tylotos
\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure30.jpg}
	\end{sideways}
	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_F_dorsal}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure31.jpg}
	\end{sideways}
	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_F_lateral}
\end{figure}

\begin{figure}[h]
	\begin{sideways}
		\centering
		\includegraphics[height=\textwidth]{figure32.jpg}
	\end{sideways}
	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_F_ventral}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure33.jpg}
	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_F_frontal}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure34.jpg}
	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_prementum}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure35.jpg}
	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_spermatheca}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{figure36.jpg}
	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
	\label{fig:tylotos_lamina}
\end{figure}
